Technical Report

### 2017-10-24 fully-abstract-comp/technical-report.tex
LR updates

%%% Logical Relation notation
\newcommand{\typesetlr}[1]{\mathcal{#1}}
\newcommand{\lre}{\typesetlr{E}}
\newcommand{\lrk}{\typesetlr{K}}
\newcommand{\lrr}{\typesetlr{R}}
\newcommand{\lro}{\typesetlr{O}}
\newcommand{\lrv}{\typesetlr{V}}

\newcommand{\stpair}[3][]{
\ifthenelse{\equal{#1}{}}
{\left(\src{#2}_S,#3_T\right)}
{\left(\src{#2},#3\right)}}

\newcommand{\memSat}[4][n]{#2 :_{#1}^{#3}#4}

@@

\section{Logical Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\lau{19-10-2017: Maybe linearity should be taken care of in just one place (instead of in $\lrr$ relation and mem staisfaction). That is, add a predicate that checks whether the configuration satisfies linearity (such a condition may be to syntactic to work?).}
In the following definitions, \src{blue} is used to indicate values related to the source machine. This is unlike previous definitions, where \src{blue} is used  indicate source language specific parts of definitions.
\[
  \lre(W) = \left\{ \npair{\stpair{v}{v}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad\src{\reg_S}(\rretd,\rretc,\pcreg) = \src{k_{d,S}}, \src{k_{c,S}}, \src{v_S} \wedge\\
      \quad\reg_T(\rretd,\rretc,\pcreg) = k_{d,S}, k_{c,S}, v_T \wedge\\
      \quad\npair[n']{\stpair[.]{(k_{d,S},k_{c,S})}{(k_{d,T},k_{c,T})}} \in \lrk(W) \wedge \\
      \quad\stpair{\reg}{\reg}\ldotp \npair[n']{
      \quad\left(\array{l}\src{\reg_S\updReg{\pcreg,\rretd,\rretc}{v_S,k_{d,S},k_{c,S}}},\\\reg_T\updReg{\pcreg,\rretd,\rretc}{v_T,k_{d,T},k_{c,T}}\endarray\right)} \in \lrr(W) \wedge\\
      \quad\src{\ms_S},\ms_T \ldotp \memSat[n']{\stpair[.]{\ms}{\ms}}{\stpair{\reg}{\reg}}{W} \\
      \quad\Rightarrow\\
      \quad\npair[n']{\left(\array{l}\src{(\reg_S\updReg{\pcreg}{v_S}\updReg{r_\ret}{k_V},\ms_S)},\\(\reg_T\updReg{\pcreg}{v_T}\updReg{r_\ret}{k_T},\ms_T)\endarray\right)}
      \in \lro(W)
    \end{array}
            \right\}
\]

@@

>>>>

%%% Logical Relation notation
\newcommand{\typesetlr}[1]{\mathcal{#1}}
\newcommand{\lre}{\typesetlr{E}}
\newcommand{\lrk}{\typesetlr{K}}
\newcommand{\lrr}{\typesetlr{R}}
\newcommand{\lro}{\typesetlr{O}}
\newcommand{\lrv}{\typesetlr{V}}
\newcommand{\lrp}{\typesetlr{P}}
\newcommand{\lrm}{\typesetlr{M}}

\newcommand{\stpair}[3][]{
\ifthenelse{\equal{#1}{}}
{\left(\src{#2_S},#3_T\right)}
{\left(\src{#2},#3\right)}}

\newcommand{\memSat}[3][n]{#2 :_{#1}#3}

@@

\section{Logical Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\lau{19-10-2017: Maybe linearity should be taken care of in just one place (instead of in $\lrr$ relation and mem staisfaction). That is, add a predicate that checks whether the configuration satisfies linearity (such a condition may be to syntactic to work?).}
In the following definitions, \src{blue} is used to indicate values related to the source machine. This is unlike previous definitions, where \src{blue} is used  indicate source language specific parts of definitions.
\[
  \lre(W) = \left\{ \npair{\stpair{v}{v}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \exists W_\lrp, W_\lrk, W_\lrr, W_\lrm \text{that is a separarion of $W$}\ldotp  \wedge \\
      \qquad\npair[n']{\stpair{v}{v}} \in \lrp(W_\lrp) \wedge \\
      \qquad\npair[n']{\stpair[.]{(k_{d,S},k_{c,S})}{(k_{d,T},k_{c,T})}} \in \lrk(W_\lrk) \wedge \\
      \qquad\npair[n']{\stpair[]{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\reg_S\updReg{\pcreg,\rretc,\rretd}{v_S,k_{c,S},k_{d,S}},\ms_S,\stk, \ms_\stk)},\\
                                          (\reg_T\updReg{\pcreg,\rretc,\rretd}{v_T,k_{c,T},k_{d,T}},\ms_T)\endarray\right)}
      \in \lro(W)
    \end{array}
            \right\}
\]
\lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but is you give a "pure" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfation does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}

@@

\[
  \lrp(W) = \left\{
    \npair{\stpair{v}{v}} \middle| \dots
  \right\}
\]
